\documentclass[10pt]{article}
\usepackage{multicol}
\usepackage{geometry}
\geometry{margin=1in}
\title{40302 Quiz}
\begin{document}
\begin{multicols}{2}
\begin{enumerate}
\item Conductors have how many valence electrons in their atoms?
	\begin{enumerate}
	\item Three to four
	\item Five to seven
	\item Eight
	\item One or two
	\end{enumerate}
\item Examples of semiconductor materials are:
	\begin{enumerate}
	\item Copper and iron
	\item Silicon and germanium
	\item Arsenic and gallium
	\item Hydrogen and oxygen
	\end{enumerate}
\item P-type and N-type materials are made by:
	\begin{enumerate}
	\item Adding electrons directly to the semiconductor.
	\item Removing electrons directly from the semiconductor.
	\item Doping the semiconductor with a substance that has five or three valence electrons.
	\item Running a current through the semiconductor.
	\end{enumerate}
\item A PN junction is what kind of electronic device?
	\begin{enumerate}
	\item Diode
	\item Rectifier
	\item OR gate
	\item SCR
	\end{enumerate}
\item \rule{1cm}{0.15mm} is the process of turning \rule{1cm}{0.15mm}.
	\begin{enumerate}
	\item Commutation, voltage into current
	\item Rectification, AC into DC
	\item Rectification, DC into AC
	\item Inversion, capacitance into inductance
	\end{enumerate}
\item Bridge rectifiers are the most common type of rectifiers used in electronic circuits.
	\begin{enumerate}
	\item True
	\item False
	\end{enumerate}
\item Peak inverse voltage (PIV) is
	\begin{enumerate}
	\item The reverse bias at which break over occurs.
	\item The forward bias at which the diode conducts.
	\item The voltage required for a diode to operate.
	\item The ratio of heat to amps characteristic.
	\end{enumerate}
\item The polarity of a diode can be confirmed by:
	\begin{enumerate}
	\item Using a voltmeter
	\item Using an ohmmeter
	\item Using an ammeter
	\item Using a caliper
	\end{enumerate}
\item LEDs emit light by which process?
	\begin{enumerate}
	\item Photosynthesis
	\item Electroluminescence
	\item Entropy
	\item Combustion
	\end{enumerate}
\item Calculate the required resistance of a current limiting resistor needed for a LED operated at 15mA with a 12V DC source.
	\begin{enumerate}
	\item 600 $\Omega$
	\item 800 $\Omega$
	\item 5 $\Omega$
	\item 90 $\Omega$
	\end{enumerate}
\item Transistors are made by joining
	\begin{enumerate}
	\item three layers of semiconductor materials.
	\item two layers of semiconductor materials.
	\item four layers of semiconductor materials.
	\item a capacitor and inductor in series.
	\end{enumerate}
\item FET devices are used in applications requiring low-impedance input and/or high power consumption.
	\begin{enumerate}
	\item True
	\item False
	\end{enumerate}
\item Phase controls use SCRs to
	\begin{enumerate}
	\item Vary the timing of a switch.
	\item Align the phases of current and voltage.
	\item Vary the amount of power delivered to a load.
	\item Ensure lights on a circuit all turn on at the same time.
	\end{enumerate}
\item Diacs can be thought of as AC switches and triacs can be used in phase control applications.
	\begin{enumerate}
	\item True
	\item False
	\end{enumerate}
\item PC (Printed Circuit Boards) use \rule{1cm}{0.15mm} instead of wires to electrically connect components.
	\begin{enumerate}
	\item tin foil bonded strips glued to the board
	\item chemically etched copper circuits
	\item gold solder lines laid onto the board
	\item None of the above.
	\end{enumerate}
\item An integrated circuit (IC) is
	\begin{enumerate}
	\item a hermetically sealed case containing a tiny wafer of semiconductor material.
	\item a PNPN connection.
	\item an operational amplifier.
	\item a device that uses optical transmission paths to transfer a signal.
	\end{enumerate}
\item A major advantage of microprocessors is its ability to provide very precise control.
	\begin{enumerate}
	\item True
	\item False
	\end{enumerate}
\item Exmamples of safe ESD working practices include:
	\begin{enumerate}
	\item Working in a carpeted area, using zip-lock bags
	\item Working in an area with tape, cardboard and plastic boxes.
	\item Using a ESD grounding strap, grounded work surface and ESD bags
	\item Using radios, and non-ESD devices in the same work area.
	\end{enumerate}
\item Op amps have which qualities?
	\begin{enumerate}
	\item High input impedance, low output impedance, low gain.
	\item Low input impedance, high output impedance, low gain.
	\item Low input impedance, low output impedance, high gain.
	\item High input impedance, low output imepdance, high gain.
	\end{enumerate}
\item Which gate gives a 0 only when both inputs are 1?
	\begin{enumerate}
	\item XAND
	\item XOR
	\item NAND
	\item OR
	\end{enumerate}
\item Which gate gives a 1 only when both inputs are 0?
	\begin{enumerate}
	\item NAND
	\item NOR
	\item AND
	\item OR
	\end{enumerate}
\end{enumerate}
\end{multicols}
\end{document}
