\documentclass[10pt]{article}
\usepackage{multicol}
\usepackage{geometry}
\geometry{margin=1in}
\title{40302 Quiz 2}
\begin{document}
\begin{multicols}{2}
\begin{enumerate}
\item A logic device that produces a logic 1 only when only one of the inputs is logic 1 is a(n):
	\begin{enumerate}
	\item Transformer
	\item AND gate
	\item OR gate
	\item XOR gate
	\end{enumerate}
\item RAM and ROM ICs are referred to as what kinds of memory, respectively?
	\begin{enumerate}
	\item Trancendental, Temporary
	\item Volatile, Non-volatile
	\item Permanent, logical
	\item Magnetic, Electric
	\end{enumerate}
\item Microprocessor controlled systems can:
	\begin{enumerate}
	\item Repair faults.
	\item Ignore faults.
	\item Recognize, isolate and report faults.
	\item Be more limited than conventional relay-based controls.
	\end{enumerate}
\item Microprocessors can be programmed to:
	\begin{enumerate}
	\item Perform complex tasks.
	\item Make decisions.
	\item Calculate mathematical results.
	\item All of the above.
	\end{enumerate}
\item IC pin identification starts with first pin at the \rule{1cm}{0.15mm} and runs \rule{1cm}{0.15cm}
	\begin{enumerate}
	\item Noth or dot, clockwise
	\item Bottom right, clockwise
	\item Notch or dot, counterclockwise
	\item Top right, counterclockwise
	\end{enumerate}
\item Silicon controlled rectifiers are made from joining:
	\begin{enumerate}
	\item Two semiconductor materials.
	\item Four semiconductor materials in a row. (PNPNP)
	\item Five semiconductor materials in a pentagon shape.
	\item A transformer with a switch.
	\end{enumerate}
\item The three lead components on a transistor are:
	\begin{enumerate}
	\item Base, Collector, Emitter
	\item Base, Giver, Receiver
	\item Home, Giver, Collector
	\item Home, Emitter, Receiver
	\end{enumerate}
\item Current flow direction in a transistor is (according to the symbol) is:
	\begin{enumerate}
	\item Opposite direction of the arrow.
	\item In the direction of the arrow.
	\item Always from emitter to collector.
	\item Always from collector to emitter.
	\end{enumerate}
\item Opto-isolators could be used becasue the circuit:
	\begin{enumerate}
	\item provides a direct physical connection between components.
	\item should be soundproof.
	\item should be dust and fireproof.
	\item is isolated from ground loop currents and voltage spikes that could damage components.
	\end{enumerate}
\item A zener diode:
	\begin{enumerate}
	\item maintains constant current at it's output.
	\item maintains constant voltate at it's output.
	\item maintains constant resistance at it's output.
	\item maintains constant reactivity at it's output.
	\end{enumerate}
\end{enumerate}
\end{multicols}
\end{document}
