\documentclass[12pt]{article}
\usepackage{adjustbox}
\usepackage{circuitikz}
\pagestyle{empty}
\textwidth 6in
\oddsidemargin 0.25in
\topmargin -0.25in
\textheight 8.5in
\begin{document}
\begin{flushleft}
Quiz
\begin{enumerate}
\item Write the three variations of Ohm's law.
\medskip
\item Write the three variations of the power equation.
\medskip
\item Write Power in terms of I and R.
\medskip
\item Find the total resistance of the following:
\begin{enumerate}
\item \begin{minipage}[t]{\linewidth}
	\adjustbox{valign=t}{%
	\input{problems/P1.tex}
}
\end{minipage}
\medskip

\item \begin{minipage}[t]{\linewidth}
	\adjustbox{valign=t}{%
	\input{problems/P2.tex}
}
\end{minipage}
\medskip

\item \begin{minipage}[t]{\linewidth}
	\adjustbox{valign=t}{%
	\input{problems/P3.tex}
}
\end{minipage}
\medskip
\end{enumerate}
\item In the previous problem define each of the given circuits (series, parallel, or series-parallel).
\medskip
\item What is the formula for calculating total resistance of four resistors in parallel?
\medskip
\item What is the formula for calculating total resistance of three resistors in series?
\medskip
\item \begin{enumerate}
\item What is the voltage commonly supplied to residential buildings?
\item What voltage is it stepped down to?
\item What component steps down the voltage?
\end{enumerate}
\medskip
\item What is measured by placing a meter across a load?
\medskip
\item Why should you make sure the circuit is turned off when checking resistance with an ohmmeter?
\medskip
\end{enumerate}
\end{flushleft}
\end{document}

